An Invariant Framework for Conducting Reproducible Computational Science

### 2015-01-15 evaluation.tex
Final

We evaluated the correctness and performance of running, packaging, and re-running the TauRoast application using Parrot and PTU.
To do this, the application was first executed directly, its execution time and output were recorded. Then the application was executed under Parrot and PTU, and a self-contained package was created for each case. Finally, the application was re-executed using the package. The time overhead of each execution and re-execution was collected and compared with the recorded reference.

The TauRoast application checks and evaluates a dataset with the size of 18 GB stored in HDFS, and can be finished in about 20 minutes when running directly on a server with 64 cores and 126 GB memory. The output of the application includes an event analysis log and a statistics information, and its size is 289 KB.

\begin{table}
\small
    \centering
    \begin{tabular}{lccc}
    \hline
    \bf Tool Type & \bf Obtain Namelist & \bf Create Package & \bf Re-Execution \\ \hline
	Parrot & 22 min 50 sec  & 4 min 25 sec & 10 min 24 sec \\ \hline
	PTU & --- & 23 min 30 sec & 8 min 40 sec \\ \hline 
    \end{tabular}
    \normalsize
    \caption{Time Comparison between Parrot and PTU}
    \label{table:parrot_ptu}
\end{table}

Table~\ref{table:parrot_ptu} compares the time overhead of preserving the TauRoast application using Parrot and PTU.
Parrot splits the packaging creation procedure into two sequential steps: first, execute the application within Parrot and generate the accessed file namelist; second, traverse the namelist and copy all the accessed files into a self-contained package.
PTU accomplishes the execution procedure and the package creation procedure concurrently through multi-threading, bringing 17.5\% additional time overhead.

The re-execution time is half or less than half of the original execution time in both cases. During the original execution, the input dataset comes from HDFS, which is accessed through FUSE. During the package creation procedure, all the input dataset has been copied from HDFS into the package on the local filesystem. So, the re-execution procedure can get its input from the local filesystem instead of obtaining the input dataset from HDFS.

@@

Table~\ref{table:size-original-real} illustrates the total size and actually used size of each source.
The total size is too large to be put into a separate image. However, the actually used size is greatly reduced to be 18 GB.
Within the package, the input dataset nearly occupies the whole package. All the other libraries and software dependencies only occupies about 200 MB.
As the input dataset grows, it can be put outside the package to reduce the shipping time of the package.

>>>>

We evaluated the correctness and performance of running, packaging, and re-running the Athena and TauRoast application using Parrot and PTU.
To do this, the application was first executed directly, its execution time and output were recorded. Then the application was executed under Parrot and PTU, and a self-contained package was created for each case. Finally, the application was re-executed using the package. The time overhead of each execution and re-execution was collected and compared with the recorded reference.

The TauRoast application checks and evaluates a dataset with the size of 18 GB stored in HDFS, and can be finished in about 20 minutes when running directly on a server with 64 cores and 126 GB memory. The output of the application includes an event analysis log and a statistics information, and its size is 289 KB. The Athena application processes a given input data file to produce four derived data files. It uses the nightly release of the Athena framework and 
submits an analysis job to obtain derived data.

\begin{table}
\small
    \centering
    \begin{tabular}{lcccc}
    \hline
    \bf Application & \bf Tool Type & \bf Obtain Namelist & \bf Create Package & \bf Re-Execution \\ \hline
	Athena & Parrot & 10 min 14 sec & 53 sec & 9 min 14 sec \\ \hline
	Athena & PTU & --- & 8min 48 sec & 7 min 21 sec \\ \hline
	TauRoast & Parrot & 22 min 50 sec  & 4 min 25 sec & 10 min 24 sec \\ \hline
	TauRoast & PTU & --- & 23 min 30 sec & 8 min 40 sec \\ \hline 
    \end{tabular}
    \normalsize
    \caption{Time Comparison between Parrot and PTU}
    \label{table:parrot_ptu}
\end{table}

Table~\ref{table:parrot_ptu} compares the time overhead of preserving Athena and TauRoast application using Parrot and PTU.
Parrot splits the packaging creation procedure into two sequential steps: first, execute the application within Parrot and generate the accessed file namelist; second, traverse the namelist and copy all the accessed files into a self-contained package.
PTU accomplishes the execution procedure and the package creation procedure concurrently through multi-threading, bringing 17.5\% additional time overhead.

The re-execution time is half or less than half of the original execution time in both cases. During the original execution, the input dataset is either locally available or comes from HDFS, which is accessed through FUSE. During the package creation procedure, all the input dataset has been copied from HDFS into the package on the local filesystem. So, the re-execution procedure can get its input from the local filesystem instead of obtaining the input dataset from HDFS.

@@

Table~\ref{table:size-original-real} illustrates the total size and actually used size of each source for TauRoast. 
The total size is too large to be put into a separate image. However, the actually used size is greatly reduced to be 18 GB.
Within the package, the input dataset nearly occupies the whole package. All the other libraries and software dependencies only occupies about 200 MB.
As the input dataset grows, it can be put outside the package to reduce the shipping time of the package.

In Athena, the input file is 224MB and output files are 16MB. PTU build a 855MB package, while Parrot builds an 825MB package. The overhead is of provenance which is 7MB and 
some differences is dependency information.

### 2015-01-15 intro.tex
Final

% Reproducibility
Reproducibility is a cornerstone of the scientific method~\cite{borgman2012data}. 
Its importance is underscored by its ability to advance science---reproducing by verifying and validating a scientific result leads to improved understanding, thus increasing possibilities of reusing or extending the result. 
Ensuring reproducibility of a scientific result, however, often entails detailed documentation and specification of the involved scientific method. Historically, this has been achieved through text and proofs in a publication. 
As computation pervades the sciences and transforms the scientific method, mere text is considered insufficient. 
In particular, apart from textual descriptions describing the result, a reproducible result must also include several computational artifacts, such as software, data,  environment variables, and state of computation that are involved in the adopted scientific method.  By including computational artifacts, the scientific result can be obtained again at a later time.

Virtualization has emerged as a promising approach for reproducing computational scientific results. One approach is to conduct the entire computation relating to a scientific result within a virtual machine image, and then share the resulting image. This way VMIs become an authoritative, encapsulated, and executable records of computations, especially computations whose results are destined for publication and/or re-use, and the VMIs can be shared easily \cite{}. 
With this approach, oftentimes, the resulting image is too big in size for share-ability purposes. An alternative light-weight form of virtualization allows encapsulation of the application software, along with all its necessary dependencies into a self-contained package, but does not make it executable.  It, thus, separates and does not include the underlying operating system on which the package is executed. The encapsulation of the self-contained package is achieved by interposing application system calls, and only copying the necessary dependencies (data, libraries, code, etc) into the package, which also makes it lighter weight than a VMI. While both forms of virtualization provide mechanisms for sandboxing the computations associated with a scientific result, neither form of virtualization provides any guarantee that the included pieces of software will indeed reproduce the associated scientific result.

Since reproducibility is significantly about comprehensive documentation, virtualization approaches in their current form only make it easy to capture the computations. Preserving the computations, so that they are easy to understand, install, or alter implicit dependencies that are part of computation, especially as dependencies and software components evolve or become deprecated, is not effectively addressed. There are two approaches to address the preservation challenge. By either introducing tools that help document dependencies and provide software attribution within VMIs or packages, or alternatively by using software delivery mechanisms, such as, centralized package management, linux containers, and the, more recent, Docker framework. We examined the first approach previously in \cite{}. In this paper we examine the second approach, that is, examine how the documentation and preservation standards that are part of software delivery mechanisms can be combined with traditional virtualization approaches for reproducibility. In particular, we consider the light-weight virtualization approaches, because, we believe that the combination of light-weight approaches with more standardized software delivery mechanisms can lead to addressing the reproducibility challenge for a wide variety of scientific researchers. 
% they may help the This  We that must also include effective  to deliver the software to a wide audience. We examine the fire
%have recently emerged  several of the reproducible challenges that arise due to use of virtualization approaches.

>>>>

% Reproducibility
Reproducibility is a cornerstone of the scientific method~\cite{borgman2012data}. 
Its importance is underscored by its ability to advance science---reproducing by verifying and validating a scientific result leads to improved understanding, thus increasing possibilities of reusing or extending the result. 
Ensuring reproducibility of a scientific result, however, often entails detailed documentation and specification of the involved scientific method. Historically, this has been achieved through text and proofs in a publication. 
As computation pervades the sciences and transforms the scientific method, mere text is considered insufficient. 
In particular, apart from textual descriptions describing the result, a reproducible result must also include several computational artifacts, such as software, data,  environment variables, and state of computation that are involved in the adopted scientific method \cite{Sole}.  By including computational artifacts, the scientific result can be obtained again at a later time.

Virtualization has emerged as a promising approach for reproducing computational scientific results. One approach is to conduct the entire computation relating to a scientific result within a virtual machine image, and then share the resulting image. This way VMIs become an authoritative, encapsulated, and executable records of computations, especially computations whose results are destined for publication and/or re-use, and the VMIs can be shared easily \cite{Lampoudi}. 
With this approach, oftentimes, the resulting image is too big in size for share-ability purposes. An alternative light-weight form of virtualization allows encapsulation of the application software, along with all its necessary dependencies into a self-contained package, but does not make it executable.  It, thus, separates and does not include the underlying operating system on which the package is executed. The encapsulation of the self-contained package is achieved by interposing application system calls, and only copying the necessary dependencies (data, libraries, code, etc) into the package, which also makes it lighter weight than a VMI. While both forms of virtualization provide mechanisms for sandboxing the computations associated with a scientific result, neither form of virtualization provides any guarantee that the included pieces of software will indeed reproduce the associated scientific result.

Since reproducibility is significantly about comprehensive documentation, virtualization approaches in their current form only make it easy to capture the computations. Preserving the computations, so that they are easy to understand, install, or alter implicit dependencies that are part of computation, especially as dependencies and software components evolve or become deprecated, is not effectively addressed. There are two approaches to address the preservation challenge. By either introducing tools that help document dependencies and provide software attribution within VMIs or packages, or alternatively by using software delivery mechanisms, such as, centralized package management, linux containers, and the, more recent, Docker framework. We examined the first approach previously in \cite{SoftProv}. In this paper we examine the second approach, that is, examine how the documentation and preservation standards that are part of software delivery mechanisms can be combined with traditional virtualization approaches for reproducibility. In particular, we consider the light-weight virtualization approaches, because, we believe that the combination of light-weight approaches with more standardized software delivery mechanisms can lead to addressing the reproducibility challenge for a wide variety of scientific researchers. 
% they may help the This  We that must also include effective  to deliver the software to a wide audience. We examine the fire
%have recently emerged  several of the reproducible challenges that arise due to use of virtualization approaches.

### 2015-01-15 measure.tex
Final

PTU~\cite{pham2014framework} is designed to create a package of an application by recording all of the binaries, libraries, scripts, data files, and environment variables used by a program.   PTU uses the CDE~\cite{guo2011cde} technology to observe system calls, but takes a snapshot of every file at the point of access.  In addition to files, PTU records \emph{metadata} about the execution environment, such as kernel versions, application versions, and dynamic library versions by using standard Unix commands.  PTU also records \emph{provenance} in the form of a graph that describes how each file is created or consumed by processes within the application.  Because PTU is focused solely on the problem of preservation, it can achieve lower overhead than Parrot when remote data access is not a requirement, as we show below.

>>>>

PTU~\cite{PTU,pham2014framework} is designed to create a package of an application by recording all of the binaries, libraries, scripts, data files, and environment variables used by a program.   PTU uses the CDE~\cite{guo2011cde} technology to observe system calls, but takes a snapshot of every file at the point of access.  In addition to files, PTU records \emph{metadata} about the execution environment, such as kernel versions, application versions, and dynamic library versions by using standard Unix commands.  PTU also records \emph{provenance} in the form of a graph that describes how each file is created or consumed by processes within the application.  Because PTU is focused solely on the problem of preservation, it can achieve lower overhead than Parrot when remote data access is not a requirement, as we show below.

### 2015-01-15 tauroast.tex
Final

We study applications taken from two experiments of the CERN Large Hadron Collider, namely the ATLAS experiment and the CMS experiment. 
One of the applications of the ATLAS experiment is the \emph{Athena} application, which is a general purpose processing framework including algorithms
for event reconstruction and data reduction. The CMS experiment is conducted through an application termed  \emph{TauRoast}, which searches for specific 
cases where the Higgs boson decays to two tau leptons~\cite{chatrchyan2013search}. In LHC, the ATLAS and CMS experiments are distinct, 
developed independently by two entirely separate physics communities. Consequently, their applications  
have very different software distribution and data management frameworks, making it interesting to examine if common reproducibility frameworks and 
tools work across the two communities.

@@

Code and data in \emph{TauRoast} is available through five different networked filesystems, namely an HDFS~\cite{borthakur2008hdfs} cluster for data files, 
some configuration files were stored on a CVMFS~\cite{blomer2011cernvm} filesystem, and a variety of software tools were on an NFS~\cite{sandberg1985design}, PanFS~\cite{welch2008scalable} and AFS~\cite{howard1988scale} systems.
In addition, code may exist in version control systems such as Git, CVS, and CMS Software Distribution (CMSSW)~\cite{cms2006cms}. 
\begin{wrapfigure}{r}{0.4\textwidth}
\small
\centering
\includegraphics[width=.4\textwidth]{data-code-size.eps}
\caption{Inputs to Tau Roast}
\label{fig:data-code-size}
\end{wrapfigure}
Data that is input to \emph{TauRoast} is obtained by reducing it through a pipeline, as shown in Figure \ref{fig:data-code-size}. Consequently, the real input data may 
vary depending upon the science question being researched. Similarly the software may name many possible components but the used components are
smaller than the named ones.

>>>>

We study applications taken from two experiments of the CERN Large Hadron Collider, namely the ATLAS experiment and the CMS experiment. 
One of the applications of the ATLAS experiment is the \emph{Athena} application, which is a general purpose processing framework including algorithms
for event reconstruction and data reduction \cite{calafiura2005athena}. The CMS experiment is conducted through an application termed  \emph{TauRoast}, which searches for specific 
cases where the Higgs boson decays to two tau leptons~\cite{chatrchyan2013search}. In LHC, the ATLAS and CMS experiments are distinct, 
developed independently by two entirely separate physics communities. Consequently, their applications  
have very different software distribution and data management frameworks, making it interesting to examine if common reproducibility frameworks and 
tools work across the two communities.

@@

Code and data in \emph{TauRoast} is available through five different networked filesystems, namely an HDFS cluster for data files, 
%~\cite{borthakur2008hdfs},~\cite{sandberg1985design},\cite{welch2008scalable}, ~\cite{howard1988scale}
some configuration files were stored on a CVMFS~\cite{blomer2011cernvm} filesystem, and a variety of software tools were on an NFS, PanFS and AFS systems.
In addition, code may exist in version control systems such as Git, CVS, and CMS Software Distribution (CMSSW). %~\cite{cms2006cms}. 
\begin{wrapfigure}{r}{0.4\textwidth}
\small
\centering
\includegraphics[width=.4\textwidth]{data-code-size.eps}
\caption{Inputs to Tau Roast}
\label{fig:data-code-size}
\end{wrapfigure}
Data that is input to \emph{TauRoast} is obtained by reducing it through a pipeline, as shown in Figure \ref{fig:data-code-size}. Consequently, the real input data may 
vary depending upon the science question being researched. Similarly the software may name many possible components but the used components are
smaller than the named ones.
